Title Goes Here

### 2020-04-14 analysis/paper/paper.Rmd
plots for 4 dimentions

Contribution of variables for each of first two PCA demensions
```{r}
PC1_v <- fviz_contrib(xx_pca, choice = "var", axes = 1, top = 7)
PC2_v <- fviz_contrib(xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(PC1_v, PC2_v, nrow =1)

>>>>

Contribution of variables for each of four PCA demensions
```{r}
library(gridExtra)

PC1_v <- fviz_contrib(xx_pca, choice = "var", axes = 1, top = 7)
PC2_v <- fviz_contrib(xx_pca, choice = "var", axes = 2, top = 7)
PC3_v <- fviz_contrib(xx_pca, choice = "var", axes = 3, top = 7)
PC4_v <- fviz_contrib(xx_pca, choice = "var", axes = 4, top = 7)

grid.arrange(PC1_v, PC2_v, PC3_v, PC4_v, nrow =2)
